Capstone Movielens Report

### 2025-12-26 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Minor fix for `UMGYDE Model`.

Now, let's construct predictors and calculate the *RMSE* score for the *current model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1195): 
```{r main-script@l1195, eval=FALSE}
cv.UMGYDE.default_params.RMSE <- cv.UMGYDE.default_params |>
  calc_UMGY_SmoothedDay_effect.RMSE.cv()
```
```{r}
cv.UMGYDE.default_params.RMSE
```

>>>>

Now, let's construct predictors and calculate the *RMSE* score for the *current model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1531): 
```{r main-script@l1531, eval=FALSE}
cv.UMGYDE.default_params.RMSE <- cv.UMGYDE.default_params |>
  calc_UMGY_SmoothedDay_effect.RMSE.cv()
```
```{r}
cv.UMGYDE.default_params.RMSE
```
